The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
some discussion added about how bad we are

% What we have presented, an independent analysis that makes maximal use of giant branch
% less-so for dwarfs
% the intent is for usefulness with chemo-dynamic studies.

>>>>

We have presented an independent re-analysis of \rave\ spectra that makes near-maximal
use of the information content for red giant branch star, and provides significant a
improvement in stellar parameter ($\teff$, $\logg$, [Fe/H]) precision over previous
\rave\ data releases.  When combined with \gaia/\tgas, these results provide a powerful
compendium for chemo-dynamic studies of the Milky Way.  However, our results have caveats.
Any inferences based upon these results should be made with the recognition of those caveats,
and acknowledge that they are subject to our explicit assumptions.

For practical purposes we adopted separate models: one for the giant branch and one
for the main-sequence.  A third model was used to derive relative weights for which
results to use.  The relative weighting we have used does not have any formal
interpretation as a likelihood or belief (in any sense): it was introduced for
practical reasons to identify systematic errors and combine results for multiple
models.  Because the relative weights have no formal interpretation, it is reasonable
to consider this method is as \emph{ad hoc} as any other approach.  Therefore, the
relative weighting has no warranty to be (formally) correct, and may introduce 
inconsistencies or systematic errors rather than
minimizing them.  Evidence of this is already present in our comparisons to
`gold standard' works \citep{Bensby_2014,Reddy_2003,Reddy_2006,Valenti_Fischer_2005},
where metal-poor dwarf stars appear as metal-poor sub-giants in our combined results,
but have reasonable labels (by any available statistic) as dwarfs in the main-sequence
model.  Clearly, the relative distance from the joint model to the giant model is 
slightly favoured (over the main-sequence model) for metal-poor dwarf stars. In this
sense, our approach towards combining labels from multiple models is sub-optimal.

If we only consider the results from individual models, there are a number of cautionary
remarks that stem from the construction of the training set.  The labels for red giant 
branch stars primarily come from \apogee, where previous successes with \thecannon\
have demonstrated that \apogee\ labels based on high S/N data can be of high fidelity.
However, the lack of metal-poor stars in the \apogee/\rave\ overlap sample produced
a tapering-off in the test set, where \emph{no} stars had reliably reported metallicities
below that of the training set, which forced us to construct a heterogeneous training
set.  The metal-poor stars included in this sample are from high-resolution studies
\citep{Fulbright,Ruchti,elsewhere}, but it is unknown if the stellar parameters are
of high fidelity (e.g., we have limited quality metrics available), and there is no
guarantee that the stellar parameters \emph{or} abundances are on the same scale as
\apogee\ \citep[and good reasons to believe they will not be; see][]{Smiljanic_2014}.
